Estimating the magnetization distribution within rectangular rock samples

### 2016-06-13 manuscript/manuscript.tex
Including paragraph describing the magnetic microscope with Hall sensor

The magnetic induction data on the four observation planes
around our synthetic sample were measured by a custom-made
magnetometer based on a Hall sensor, whose circular
effective area has a diameter of $\approx$~$300$~$\mu$m.
The equipment is under development at the Pontifical Catholic 
University of Rio de Janeiro (PUC-Rio), in Brazil, and
the experimental measurements were made without any 
magnetic shielding, then it is important to bear in mind 
the possible bias in these data.

On each plane $\alpha = 0, 1, 2, 3$, the magnetic data were 
measured at a constant distance $h \approx 500$~$\mu$m, on
a regular grid of $102 \times 42$ points along the $x$ and 
$y$/$z$ axes, respectively (Figures \ref{fig:datafit-real}a,
d, g and j).

>>>>

The magnetic induction data on the four observation planes around our synthetic sample were measured by a scanning Hall magnetic microscope, developed at Pontifical Catholic University of Rio de Janeiro (PUC-Rio), in Brazil. It is based on a commercial GaAs Hall-effect sensor (HG-176A, AKM Inc.) that detects the remanent magnetic field normal to the scanning plane. The sensor has an active area size of $300 \, \mu m$, which is $250 \, \mu m$ distant from the top of the encapsulation. The maximum spatial resolution achieved is about the size of the sensor’s active area. The magnetic field sensitivity measured is $350 \, nT/Hz^{1/2}$ in the white noise region. The sensor is current biased and pre-amplified by a custom-made electronics at $1.0 \, kHz$, and the output Hall voltage is detected by a lock-in amplifier. In our microscope, two independent linear micropositioners (T-LLS260, Zaber Technologies) were oriented perpendicularly and stacked, making up an $x-y$ stage with a maximum travel range of $50 \, mm$ in each direction. An acrylic pedestal, $15 \, mm$ long, is fixed to the stage, serving two purposes, providing a flat surface for the sample to be mounted to and increasing the distance from the sample to the micropositioners’ motors minimizing inductive effects. The sensor is mounted on another acrylic rod that can be raised or lowered using a linear actuator (T-LA60A, Zaber Technologies), allowing for the adjustment of the sensor to sample distance with micrometer accuracy. The scanning of the sample is made in a stop-and-go system, meaning that when the sample is moved to a scanning position, it stops for the magnetic field measurement and only then, it goes to the next position. In order to reduce environmental magnetic noise present at the laboratory, the experimental measurements were made inside a small 3 layer open-end magnetic shielded chamber (TLM S-0100, Bartington Instruments). We used for scanning a step of $200 \, \ mu m$ in both $x$ and $y$ directions. On each plane $\alpha = 0, 1, 2, 3$, the magnetic data were measured at a constant distance $h \approx 500$~$\mu$m, on a regular grid of $102 \times 42$ points along the $x$ and $y$/$z$ axes, respectively (Figures \ref{fig:datafit-real}a, d, g and j).
